### 2012-11-09 inst/examples/compare-cholesky.Rmd
updated comparing-methods plots

## Compare Cholsky and Direct methods

@@

  ## Cholksy method -- Consider implementing in C
  L <- chol(K + sigma_n ^ 2 * I)
  alpha <- solve(t(L), solve(L, obs$y))
  loglik <- -.5 * t(obs$y) %*% alpha - sum(log(diag(L))) - n * log(2 * pi) / 2
  k_star <- cov(obs$x, X)
  mu <- t(k_star) %*% alpha
  v <- solve(L, k_star)
  var <- diag( cov(X,X) - t(v) %*% v )

  ## Pt by pt following Rassmussen & WIlliams, but there's no reason to do it this way
#  tmp <- lapply(X, function(x_i){  
#    k_star <- cov(obs$x, x_i)
#    Y <- t(k_star) %*% alpha
#    v <- solve(L, k_star)
#    Var <- cov(x_i,x_i) - t(v) %*% v
#    list(Y=Y, Var=Var)
#  })
#  mu <- sapply(tmp,`[[`, "Y")
#  var <- sapply(tmp,`[[`, "Var")

>>>>

## Compare Cholesky and Direct methods
```{r settings}
opts_knit$set(upload.fun = socialR::notebook.url)
```

@@

  ## Cholesky method -- Consider implementing in C
  L <- chol(K + sigma_n ^ 2 * I)
  alpha <- solve(t(L), solve(L, obs$y))
  loglik <- -.5 * t(obs$y) %*% alpha - sum(log(diag(L))) - n * log(2 * pi) / 2
  k_star <- cov(obs$x, X)
  mu <- t(k_star) %*% alpha
  v <- solve(L, k_star)
  var <- diag( cov(X,X) - t(v) %*% v )

## Pt by pt following Rassmussen & Williams, but there's no reason to do it this way
#  tmp <- lapply(X, function(x_i){  
#    k_star <- cov(obs$x, x_i)
#    Y <- t(k_star) %*% alpha
#    v <- solve(L, k_star)
#    Var <- cov(x_i,x_i) - t(v) %*% v
#    list(Y=Y, Var=Var)
#  })
#  mu <- sapply(tmp,`[[`, "Y")
#  var <- sapply(tmp,`[[`, "Var")

### 2012-11-09 inst/examples/comparing-methods.Rmd
updated comparing-methods plots

```{r include=FALSE}
sha <- gsub("^commit ", "", system("git log -n 1", intern=TRUE)[1])
short_sha <- gsub("(^.{10}).*", "\\1", sha)
date <- format(Sys.time(), "%Y-%m-%d")
fig.path = paste("../../../assets/figures/", date, "-", short_sha, "-", sep="")
opts_chunk$set(fig.path=fig.path)
theme_publish <- theme_set(theme_bw(14))
theme_publish <- theme_update(
        # panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        legend.title=theme_blank(), 
        panel.background = theme_rect(fill = "transparent",colour = NA), 
        plot.background = theme_rect(fill = "transparent",colour = NA))
```

```{r}
require(MASS)
require(ggplot2)
require(kernlab)
```

@@

Cholksy method

>>>>

```{r}
require(MASS)
require(ggplot2)
require(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
```

@@

Cholesky method
